--- 
title: "On the growth of the Swedish Forests"
swedishtitle: "Om tillväxten i de Svenska Skogarna"
subtitle: "From the heights of inner Norrland to the Westrobothnian coast"
swedishsubtitle: "Inre Norrlands Höglid till Västerbottniska kusten"
author: "Carl Vigren"
faculty: "Forest Sciences"
department: "Forest Ecology and Management"
swedepartment: "Institutionen för Skogens Ekologi och Skötsel"
address: "Skogsmarksgränd 17, 901 83 Umeå"
email: "carl.vigren@slu.se"
thesistype: "DOCTORAL THESIS"
submitplace: "Umeå"
submityear: "2021"
date: "`r Sys.Date()`"
serialnumber: "Serial number XXX "
coverphoto: "Cover photo description."
issn: "ISSN"
isbnPrint: "ISBN Print"
isbnElectronic: "ISBN Electronic"
printplace: "Uppsala"
abstracttitle: "English abstract title"
abstract: "abstract"
keywords: "keywords"
swedishabstracttitle: "Swedish abstract title"
swedishabstract: "The swedish abstract version"
nyckelord: "Nyckelord"
dedication: "To all those who helped me."
popularvetenskapligsammanfattning: "Svenska som folk förstår här."
graphics: true #don't touch
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
output:
  bookdown::pdf_book:
    includes:
      in_header: "preamble.tex"
    template: template.tex
font-family: helvet
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
